MCC Models

### 2019-08-08 papers/full_paper/SI_appendix.Rmd
subscripting typo
fix typos

\noindent where \mathcal{L}_{point} encodes the meaning of the actions (points), and is simply a truth-function stipulating the location of the referent must be at the location of the point / turn.
We assume in this model that the speaker is trying to convey the type of the referent $r^t$ rather than the individual token referents $r^i$; thus, the relevant probability for purposes of informativity is the type probability $P_{L_0}(r^t|u)$, which is simply a sum of the token probabilities for tokens that are of the same type $ \sum_{r_i \in t} P_{L_0}(r_i | u)$.

>>>>

\noindent where $\mathcal{L}_{point}$ encodes the meaning of the actions (points), and is simply a truth-function stipulating the location of the referent must be at the location of the point / turn.
We assume in this model that the speaker is trying to convey the type of the referent $r^t$ rather than the individual token referents $r^i$; thus, the relevant probability for purposes of informativity is the type probability $P_{L_0}(r^t|u)$, which is simply a sum of the token probabilities for tokens that are of the same type $\sum_{r_i \in t} P_{L_0}(r_i | u)$.
